Python as a machine learning language: experiences from the \sklearn project

### 2013-06-10 paper.tex
clarify pipeline fitting
Also, the concept of "grid-searching" is not yet introduced.

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data; however,
\texttt{predict} can also be called on \texttt{X\_train}). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
from sklearn.cluster import KMeans
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \sklearn thus offers a unified way
to compute predictions with respect to unseen data.

@@

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
centering / scaling / normalization, feature selection, learning and making
predictions). For convenience reasons, those steps can be combined into a
pipeline such that \texttt{fit} and \texttt{predict} need to be called only once
to fit the whole sequence. A pipeline also allows for the hyper-parameters of
all the base estimators to be grid-searched all at once. From an API point of
view, a \texttt{Pipeline} object takes as input a sequence of $N$ estimators,
where all $N-1$ first are transformers and the last is either a predictor or a
transformer. Calling \texttt{fit} on the pipeline is the same as calling
\texttt{fit} on each estimator in turn, \texttt{transform} the input and then
pass it on to the next step. The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can be used itself as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}

>>>>

\textbf{Predictors.} The \textit{predictor} interface defines a \texttt{predict}
method taking as input some new data \texttt{X\_test} and producing as output
predictions for \texttt{X\_test}, based on the learned parameters of the
estimator (we call the input to \texttt{predict} ``\texttt{X\_test}'' in order
to emphasize that \texttt{predict} generalizes to new data). In the case of
supervised learning estimators, this method typically returns the predicted
labels or values computed by the model.  Continuing with the previous example,
predicted labels for \texttt{X\_test} can be obtained using the following
snippet:
\begin{verbatim}
y_pred = clf.predict(X_test)
\end{verbatim}
Some unsupervised learning
estimators may however also implement that interface, as illustrated below:
\begin{verbatim}
from sklearn.cluster import KMeans
km = KMeans(n_clusters=10)
km.fit(X_train)
clust_pred = km.predict(X_test)
\end{verbatim}
In the above example, a \texttt{KMeans} estimator is first fit on the training
data \texttt{X\_train}. Then the \texttt{predict} method is called on the test
data \texttt{X\_test} in order to retrieve predicted cluster labels.
The \texttt{predict} method in \sklearn thus offers a unified way
to compute predictions with respect to unseen data.

@@

\texttt{Pipeline} objects are used for chaining multiple estimators into a
single one. This is useful since a machine learning workflow typically involves
a fixed sequence of steps in processing data (e.g., feature extraction,
normalization, feature selection, learning and making predictions).
A sequence of $N$ such steps can be combined into a composite object
called a \texttt{Pipeline}.
The first $N-1$ steps must be transformers
and the last can be either a predictor or a transformer.
Fitting a pipeline to a training set amounts, conceptually,
to the following recursive procedure:
\begin{enumerate}
  \item When only one step remains, call its \texttt{fit} method.
  \item Otherwise, fit the first step,
        use it to \texttt{transform} the training set
        and fit the rest of the pipeline with the transformed data.
\end{enumerate}
The pipeline exposes all the methods the last
estimator in the pipe exposes. That is, if the last estimator is a predictor,
the pipeline can itself be used as a predictor. If the last estimator is a
transformer, then the pipeline is itself a transformer. \textcolor{red}{TODO:
Talk about nested attribute syntax.}
